---
title: "Classwork Worksheet 1"
output: html_document
author: YOUR NAME HERE
date: "2026-07-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions

1. What is the area of research in which you want to do your project?

```{r}

```


2. Name a possible data set of interest for your topic. If you are analyzing data you created or from a past research project, describe it in terms of domain and scope.If it is a publicly available dataset, provide a URL. 

```{r}

```

3. What if any restrictions are there on access? Are there fees? Do you have to register? Who is allowed to access this data? 

```{r}

```

4. How many records does the data you are interested in contain?

```{r}

```


5. How many variables? 

```{r}

```

6. What possible research questions could you ask? This does not need to be a fleshed out PICO style question, but what generally may be worth exploring in this data?

```{r}

```

7. What is the relevance of your research question?

```{r}

```

8. What may be challenges or limitations in working with this data source? 

```{r}

```

9. Are there possible ethical challenges?

```{r}

```


## NYC HANES Diabetes subset Questions

10. How many records or observations does the NYC HANES diabetes subset dataset contain?

```{r}

```

11. How many variables are contained in it? 

```{r}

```

12. If we had a csv file of this data, what command might we run to load it?

```{r}

```

13. We receive an error when we run try to get the average age (SPAGE) by running the following:

> Mean(nyc$spage)

What possible solutions could we try to get this to run?

```{r}

```

14. What are some sources of information we might use to look up how to solve 13?

```{r}

```


15. How would we add a comment to explain we were taking the average of age?

```{r}

```

