---
title: "Classwork Worksheet 5"
output: html_document
author: YOUR NAME HERE
date: "2026-07-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1 pt per question


## Questions

1. Describe two visualizations you want to include in your final talk. Why are you including them? What variables are included? What chart type (geom) may be illustrate your goal?

```{r}

```

2. Provide the code to make the charts you describe above.

```{r}

```


# General Questions


```{r}
nyc <- read.csv("https://raw.githubusercontent.com/fredlapolla/VilcekSummerDataAnalysis2024/main/NYC_HANES_DIAB.csv")
```



3. Using GGplot, make a boxplot of A1C by diabetes diagnosis. Would you assume the three groups have the same A1C level? 

```{r}

```


4. Use ggplot2 to make a scatter plot of A1C by glucose levels.

```{r}

```


5. Add coloration by gender for the above scatter plot and change the background theme to the minimal option. Change the X axis to label numbers by increments of 3. 

```{r}


```

6. Create a GGPlot chart of Lead vs. Cotinine and show two different themes for the background. 

```{r}


```

7. Make bar charts of mean Glucose level by diabetes diagnosis. Add error bars.

```{r}

```


8. Where could you go to look up other Geom shapes for different types of charts?

```{r}

```
