---
title: "Classwork Worksheet 1"
output: html_document
author: YOUR NAME HERE
date: "2026-07-13"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Questions

1.What dataset are you working with for your final and provide a brief synopsis of what it contains? 

```{r}

```

2. What is a research question of interest to you relating to this data? Provide the question in a PICO format: Problem/Population Intervention/Exposure Comparison Outcome. https://pmc-ncbi-nlm-nih-gov.ezproxy.med.nyu.edu/articles/PMC11129835/ 

```{r}

```


3. Does this question meet the FINER criteria? Break down letter by letter to demonstrate. https://pmc-ncbi-nlm-nih-gov.ezproxy.med.nyu.edu/articles/PMC11129835/

```{r}

```



4. What variables are relevant to your research question?

```{r}

```


5. Demonstrate how you would use ifelse() to make a given continuous variable into a dichtomous factor variable

```{r}

```





## NYC HANES Diabetes subset Questions

Data can be accessed at: https://raw.githubusercontent.com/fredlapolla/VilcekSummer26/refs/heads/main/NYC_HANES_DIAB.csv

6. Use apply() to find the median value of CADMIUM, LEAD CHOLESTEROLTOTAL, GLUCOSESI, CREATININESI, and CREATININE

```{r}

```


7.  Do the same using sapply()

```{r}

```

8. Use a for loop to find the median value of columns 16:19

```{r}

```


9. Make a for loop to find the standard deviation (hint sd() ) of CHOLESTEROLTOTAL, GLUCOSESI, CREATININESI, AND CREATININE

```{r}

```




10. Use ifelse to create a new variable of high and normal A1C dichotomizing with 7 as a threshold for high levels

```{r}


```
