---
title: "Classwork Worksheet 9"
output: html_document
author: YOUR NAME HERE
date: "2026-08-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1 pt per question


## Questions

1.What direct comparisons would you like to make to understand more about your data? By direct comparisons, I mean two variables like examining if cholesterol levels differ by age. List the bivariate pairs, and what comparing them will tell you. 

```{r}

```

2. What types of data are contained in the variables you have listed above (e.g. numeric, factor). Explicitly state what type of data for each variable. 

```{r}

```

3. What types of tests are appropriate for each bivariate pair, and why?

```{r}

```

4. What is the main inference you are trying to make in your presentation (e.g. Does increased age correlate with higher cholesterol)?

```{r}

```

5. Provide the code for how to examine that question as a bivariate test. 

```{r}

```

6. Provide the code for the additional comparisons you are making, that you listed in question 1. The purpose here is to consider if additional variables may have a relationship with your main question.

```{r}

```

