---
title: "Classwork Worksheet 5"
output: html_document
author: YOUR NAME HERE
date: "2026-07-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1 pt per question


## Questions

1.Using your final project data, identify three variables of interest and assess if they are normal or not using....

a) A Histogram

```{r}

```

b) A Boxplot

```{r}

```

c) A QQ Plot

```{r}

```

2) If you data features continuous variables, visualize any potential correlations. If not, provide the command you would use to visualize correlations.

```{r}

```

## Additional Questions

Use the following data for the next questions:
https://raw.githubusercontent.com/fredlapolla/VilcekSummer26/refs/heads/main/NYC_HANES_DIAB.csv

3. Why would one use a visualization for exploratory analysis?



4.What information about the nature of our data can a histogram tell us?


5. Make a histogram on LEAD from the nyc data frame. Is it skewed? Which way? 

```{r}

```

6. Make a QQPlot to assess the normality UCREATININE. Is the distribution normal? How can you tell?

```{r}

```

7. Make a boxplot glucose levels by diabetes diagnosis:

```{r}

```

8. Make a scatterplot of total cholesterol by LDL. Does there appear to be a relationship?

```{r}

```
