---
title: "Classwork Worksheet 5"
output: html_document
author: YOUR NAME HERE
date: "2026-07-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1 pt per question


## Questions

1.Is your data in a tidy format or another format? Explain what makes it tidy or not. 

```{r}
```

2. Provide the code for how you have made a subset of your data and explain why you have subsetted it in that way. For example, maybe you are simplifying down to key variables for simplicity, or looking at a subset of records, such as to investigate NAs or to analyze a specific group. 

```{r}

```

3. Has your research question changed? Please state your current question in PICO format. 

```{r}
 
```

## Worksheet Questions

Use the Synthetic Mass Data:

Observations: https://raw.githubusercontent.com/fredlapolla/VilcekSummer26/refs/heads/main/observations.csv

Patients: https://raw.githubusercontent.com/fredlapolla/VilcekSummer26/refs/heads/main/patients.csv

Medications: https://raw.githubusercontent.com/fredlapolla/VilcekSummer26/refs/heads/main/medications.csv

Conditions: https://raw.githubusercontent.com/fredlapolla/VilcekSummer26/refs/heads/main/conditions.csv

4. Make a subset of Patient data to have patient ID, sex/gender, race and ethnicity. 

```{r}

```

5. Make a subset of observation data for body weight and body height, and filter to have only the most recent of each. 

```{r}


```

6. Convert the body weight and height tables to wide format. 

```{r}


```

7. Merge the body weight and height information onto your demographic dataframe created in question one. 

```{r}

```

8. Calculate BMI into a new column. The equation is weight (kg)/height ^2 (m)

```{r}

```



