---
title: "Classwork Worksheet 1"
output: html_document
author: YOUR NAME HERE
date: "2026-07-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1 pt per question


## Questions

1.Why would one want to provide a code like 777 or 999 for a missing value?

```{r}

```

2. In the variables you have identified as of interest in your data, are missing variables coded any specific way? If so provide code for how to recode those variables. 

```{r}


```


3. In the variables of interest, how many missing values are present? What is the proportion of missing values? Do you anticipate this impacting your analysis decisions?

```{r}

```


4.Provide code showing how you have recoded any incorrectly coded variables (e.g. numeric to factor)

```{r}

```




## NYC HANES Diabetes subset Questions

Data can be accessed at: https://raw.githubusercontent.com/fredlapolla/VilcekSummer26/refs/heads/main/NYC_HANES_DIAB.csv



5. Create a subset of males and find the median total cholesterol level

```{r}

```


6. Try to create a summary of the mean A1C using two factors, GENDER and DX_DBTS (e.g. A1C for males without diabetes, A1C for males with diabetes,A1C females without,A1C females with)

```{r}

```


7. How does R treat blank values?

```{r}

```


8. What command can be used to identify where NAs are located in a column?

```{r}

```


9. How can you use indexing to create a subset without any NAs?

```{r}

```

10. How could you delete a column of data, for example, the 5th 

```{r}

```
