---
title: "Classwork Worksheet 1"
output: html_document
author: YOUR NAME HERE
date: "2026-07-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1 pt per question


## Questions

1.Provide a simple file naming plan for keeping your analysis files organized

```{r}

```

2. How can using an R project help keep your analysis files organized?

```{r}

```

3. If using AI for code generation, what are some analysis risks?

```{r}

```


## NYC HANES Diabetes subset Questions

Data can be accessed at: https://raw.githubusercontent.com/fredlapolla/VilcekSummer26/refs/heads/main/NYC_HANES_DIAB.csv

4. Provide three ways to get an overview/sense of data in your nyc hanes dataset:

```{r}

```

5. What is the structure of your nyc data?

```{r}

```

6. Before cleaning data what is the class of the column AGEGROUP?

```{r}

```

7. What data type seems most appropriate for AGEGROUP?

```{r}

```

8. How do we recode AGEGROUP to that data type?

```{r}

```

9. Why might we want to use labels for different categories, e.g. Youngest, Middle or Aged as opposed to 1,2, and 3.

```{r}

```

10. What differentiates a matrix from a data frame?

```{r}

```

