---
title: "Data Analysis with R 7: Bioinformatics Visualization"
author: "Fred LaPolla"
date: "7/23/2026"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Heatmaps

### Acknolwedgements:

The following is borrowed from Dr. Itai Yannai and Dr. Igor Dolgalev

***

## Heatmaps

In looking at gene expression data you may want to see a heatmap to see which timepoints/genes are being expressed. A heatmap is a quick way to look at large volumes of data by highlighting cells that have higher or lower values in them. 

```{r, echo = TRUE}
dolgalevNormRNA <- read.csv("https://raw.githubusercontent.com/fredlapolla/VilcekSummer26/refs/heads/main/counts.normalized.csv")

```


***

## Checking our data

This data provided by Dr. Dolgalev is a table of RNA-seq normalized counts. These are expression values of all genes across different samples. There are wild-type and Tet2-knockout samples (4 of each).
 
For more details on how the table was generated, the steps are summarized here:
http://bit.ly/snsdemo

```{r, echo = TRUE}
head(dolgalevNormRNA)
class(dolgalevNormRNA)

```

We can see column 1 is the gene name, column 2, 3 and 8 and 9 are the Wild Type samples, and columns 4:7 are the knock out samples. 

***

## Reordering to group by type

```{r}
dolgalevNormRNA<- dolgalevNormRNA[c(1:3,8:9, 4:7)]
head(dolgalevNormRNA)
dolgaMat <- as.matrix(dolgalevNormRNA[,2:9], "numeric")
rownames(dolgaMat)<- dolgalevNormRNA[,1]
head(dolgaMat)
class(dolgaMat)
class(dolgaMat[,1])
summary(dolgaMat)
```


***
## Creating a heatmap of KnockOut vs Wild Type

```{r}


exp_genesAll <- names(which(rowSums(dolgaMat)>15000))


dolgaExp <- dolgaMat[exp_genesAll,]

```



***


```{r}
#if (!require("BiocManager", quietly = TRUE))
   # install.packages("BiocManager")

#BiocManager::install("ComplexHeatmap")
library(ComplexHeatmap)
Heatmap(dolgaExp)

```

```{r}
Heatmap(dolgaExp, cluster_columns = FALSE, clustering_method_rows = "complete", show_row_names = FALSE)

```


***

## Clustering a pairwise correlation of expressions:

We might look at a heatmap of the highly expressed genes. Explore cor() in RStudio, what does this command do? What is t()? Why are we taking the t() of our matrix?  

```{r}

Heatmap(cor(t(dolgaExp)), show_column_names = FALSE, show_row_names = FALSE)

```

Then we can take this figure, and using a command called hclust, we can pass a method we want the clustering to be done. dist means it is creating a "distance matrix" of the correlations of gene expression, which is a way of saying if we were to chart the values, how far would each be from one another. You can explor ways you can cluster by viewing ?dist. Then this 

```{r}


##A correlation of the highly expressed genes in our set
Cormat <- cor(t(dolgaExp))
#then it becomes a heatmap
hotdog <- Heatmap(Cormat)
print(hotdog)

```


```{r}
## We cluster the values in this set of gene expression using euclidian distance
## Basically on the backend, R is making a matrix of the values in C and then calculating
##How far they are from one another
heirdog <- hclust(d=dist(Cormat))

## Then we are choosing where to cut the dendrogram, here 6 "branches" or groups have
## been cut, you could also choose to cut the dendrogram by height using h instead of K
heirchop <- as.factor(cutree(heirdog, k=6))
## Now we make a heatmap again using the order of the clustering
hotterdog = ComplexHeatmap::Heatmap(Cormat[heirdog$order, heirdog$order],cluster_rows=FALSE, cluster_columns=FALSE)
## Finally we add annotations to show the groups that we have made
annodog = HeatmapAnnotation(df = data.frame(heirchop[heirdog$order]), which = 'row')
print(hotterdog+annodog)

```


*** 





We can also use several methods of hierarchical clustering in our chart. To learn more about these try: ?hclust  

```{r}
Heatmap(Cormat, clustering_method_rows = "complete", cluster_columns = FALSE )
```



***



```{r}
#install.packages("RColorBrewer", repos = "http://cran.us.r-project.org")
library(RColorBrewer)
Heatmap(Cormat, col = brewer.pal(7,"BuGn"))
```

***


## Unsupervised Clustering

You can also use a command kmeans() for unsupervised clustering:

```{r}
kRes <- kmeans(t(Cormat),  10)
hist(kRes$cluster)
```

